Constructing Biological Regulatory Networks from Process Hitting models

### 2013-07-05 parts/infer-ig.tex
typos + suppr urls from bib

\updated{%
In a typical biological network modelling process, a prior IG is generally the starting point for
the formal system specification.
However, it is very common that the prior IG actually refers interaction that reveal to be 
non-effective with respect to the dynamics.
Hence, deriving the IG directly from the dynamical models lead to more concise IGs, enhancing the
conclusiveness of static analyses based upon this abstract representation.}

@@

\todo{remark for reducing the number of self-regulation}

>>>>

\updated{%
In a typical biological network modelling process, a prior IG is generally the starting point for
the formal system specification.
However, it is common that the prior IG actually refers to interactions that reveal to be 
non-effective with respect to the dynamics.
Hence, deriving the IG directly from the dynamical models lead to more concise IGs, enhancing the
conclusiveness of static analyses based upon this abstract representation.}

@@
